\section{Introduction}

% previously context and problem

The growth of audiovisual content has driven the development of methods capable of analyzing, indexing, and automatically retrieving visual information. In this context, multimodal video-text retrieval has established itself as a relevant area at the intersection of computer vision and natural language processing. An especially challenging scenario for these tasks is that of egocentric video, which captures activities from a first-person perspective using body- or head-mounted cameras. This type of video records natural interactions between hands, objects, and the environment, introducing high visual and temporal variability. Consequently, models must be able to interpret actions and contextual relationships in order to establish precise correspondences between visual content and its textual description. 

Despite recent advances in multimodal models, semantic alignment between video and natural language remains challenging, particularly in egocentric scenarios. These videos are characterized by constant perspective changes, occlusions, and multiple object interactions which makes it particularly difficult to extract robust visual representations. Furthermore, in multimodal retrieval tasks a single video may be related to multiple descriptions at different levels of similarity. This requires models capable of estimating continuous semantic relations between video and text, going beyond approaches based solely on binary correspondences. It is therefore necessary to develop methods that integrate visual and textual representations in a shared semantic space, enabling more precise modeling of the relationships between observed actions and natural language descriptions.

One of the most relevant resources for this problem is the \href{https://epic-kitchens.github.io/}{\textit{EPIC-KITCHENS-100}} dataset, which contains over 100 hours of egocentric video in real domestic environments and approximately 90\,000 annotated segments. The \href{https://www.codabench.org/competitions/12008/#/pages-tab}{\textit{EPIC-KITCHENS-100 Multi-Instance Retrieval Challenge}} is built on this dataset; its goal is to align video clips and textual descriptions through relevance matrices with soft labels, allowing different degrees of semantic similarity between video--text pairs to be modeled.

This project contributes to the study of deep learning methods for semantic alignment between video and natural language in egocentric scenarios and presents a fine-tuned \textbf{TBD baseline model} using a \textbf{TBD Loss function spec} and a novel contextual embedding technique \textbf{TBD specifications}. These results allow an exploration of strategies to generate multimodal representations capable of modeling different degrees of similarity between both modalities. Advances in these methods can facilitate the development of search and automatic organization systems for large video repositories, as well as applications in intelligent assistants based on egocentric vision and automated human activity analysis.
